### 2024-01-15 README.Rmd
upated RMD - 240110
new laptop push

The goal of `validateHOT` is to provide a tool to validate the results
of your validation task (also known as holdout task; short form
**HOT**), simulating markets with the results of your MaxDiff, CBC, and
ACBC, and lastly converting the raw logit scores of your MaxDiff, CBC,
and ACBC into scores that are easier to communicate. This package is
especially relevant for the [Sawtooth
Software](https://sawtoothsoftware.com/) community who would like to
report their analysis in *R* for open science purposes. However, it also
works perfectly with the package `ChoiceModelR`(Sermas, 2022). This
package is extremely useful for practitioners, who would like to run the
analyses in an open source software. The ultimate goal of these
preference measurement techniques is to predict future behavior (Green &
Srinivasan, 1990). Therefore, it is essential for both academics and
practitioners to ensure that the collected data is valid and can also
predict outside tasks that were not included in the estimation of the
utility scores.

@@

<li><code>kl()</code>: Kullback-Leibler-Divergence measures the
divergence between the actual choice distribution and the predicted
choice distribution (Ding et al., 2011; Drost, 2018). Output provides
both divergence between predicted from observed and observed from
predicted due to the asymmetry of the Kullback-Leibler divergence.
`validateHOT` currently provides two logarithm bases: \eqn{log} and
\eqn{log{_2}}. The default is set to \eqn{log}.</li>

>>>>

The goal of `validateHOT` is to provide a tool to validate the results
of a validation task (also known as holdout task; short form
**HOT**), simulating markets with the results of your MaxDiff, CBC, and
ACBC, and lastly converting the raw logit scores of your MaxDiff, CBC,
and ACBC into scores that are easier to communicate. This package is
especially relevant for the [Sawtooth
Software](https://sawtoothsoftware.com/) community who would like to
report their analysis in *R* for open science purposes. However, it also
works perfectly with the package `ChoiceModelR`(Sermas, 2022). This
package is extremely useful for practitioners, who would like to run the
analyses in an open source software. The ultimate goal of these
preference measurement techniques is to predict future behavior (Green &
Srinivasan, 1990). Therefore, it is essential for both academics and
practitioners to ensure that the collected data is valid and can also
predict outside tasks that were not included in the estimation of the
utility scores.

@@

<li><code>kl()</code>: Kullback-Leibler-Divergence measures the
divergence between the actual choice distribution and the predicted
choice distribution (Ding et al., 2011; Drost, 2018). Output provides
both divergence between predicted from observed and observed from
predicted due to the asymmetry of the Kullback-Leibler divergence.
<code>validateHOT</code> currently provides two logarithm bases: $log$
and $log_2$. The default is set to $log$.</li>
